### 2023-04-03 README.Rmd
Grammar correction
name update
updated readme

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# MethodPaper

@@

> Sjoelander Mattias, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Sjoelander Mattias, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Sjoelander Mattias, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

## How to run in your broswer or download and run locally

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Quartzite Complexities: Non-destructive analysis of bifacial points from Västerbotten, Sweden"
```

# Quartzite Complexities: Non-destructive analysis of bifacial points from Västerbotten, Sweden

@@

> Sjölander M., Linderholm, J., Geladi P (2023). _`r Title`_. Journal of Archaeological and Anthropological Sciences <https://doi.org/xxx/xxx>

The pre-print is online here:

> Sjölander M., Linderholm, J., Geladi P (2023). _`r Title`_. Journal of Archaeological and Anthropological Sciences `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Sjölander M., Linderholm, J., Geladi P (2023). (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

## How to run in your browser or download and run locally
